### 2019-11-06 report/paper.tex
add experiments
add first part of experiments

\documentclass[11pt]{article}
\usepackage[OT4]{fontenc}
\newtheorem{define}{Definition}
\usepackage{graphicx}
\usepackage{subcaption}
\oddsidemargin=0.15in
\evensidemargin=0.15in
\topmargin=-.5in
\textheight=9in
\textwidth=6.25in

@@

Specify how to process the data, how to evaluate the performance (e.g., mAP).
\begin{table}[ht]
    \centering
    \begin{tabular}{l|c|c|c}
    \hline
     Dataset & \#train & \#test & \#Category\\
    \hline
    MNIST& 60,000 & 10,000 & 10  \\
    CIFAR-10& 50,000 & 10,000 & 10 \\
    \hline
    \end{tabular}
    \caption{Summary of datasets.}
    \label{tab:dataset}
\end{table}

\subsection{Implementation}
Give a figure to illustrate your implementation, then detail each parts.

>>>>

\documentclass[11pt]{article}
\usepackage[OT4]{fontenc}
\newtheorem{define}{Definition}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{booktabs}
\oddsidemargin=0.15in
\evensidemargin=0.15in
\topmargin=-.5in
\textheight=9in
\textwidth=6.25in

@@

\begin{figure}[]
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after kemans preprocessing (originally gray-cale, but color mapped for display purposes)}
    \label{fig:preprocessed-samples}
\end{figure}

The images in the dataset come as annotated bounding boxes of varying aspect ratios and sizes in pixels.
Also the size of the respective images changes as well. Therefore we simplified the detection process by
generating \( (128 \times 128) \) px training images from the provided bounding boxes. 
Doing so resulted in some croping to the actual characters appearances, which cannot be avoided in some corner cases.
However in general we were able to regularize the bounding boxes without loosing any pixels belong to the positive annotations.
See \autoref{fig:preprocessed-samples} for examples of the cropped and scaled input images.

To map the color images as robustly as possible to gray scale values we used a K-Means detector 
and assigned each of the modes an equally gray spaced color. 
K-Means works by intially choosing random starting points in the image and then projecting an area around them, calculating the "center of gravity"
of those inlier points and then shifting the new centroid to this "center of gravity". When repeating this
process until convergence \( k \) such different means are found. This process results in a non-uniform quantization of the input image.

We use this property to train the K-Means classifier on a sample image of the \verb|wenda| class, which only 
shows the colors red, blue, black white. However we use \( k=5 \) to classify any color not lying in these four as a separate class, and then merge 
its results with the white color class. Then these four resulting classes colored centroids are mapped to uniformly
chosen values \( v \in [0, 255] \). This drastically reduces the complexity of the input images as can be seen in the right image in \autoref{fig:preprocessed-samples},
reducing input noise when processing the images with our feature descriptor in \autoref{sec:implemenation}.

\vspace{0.5cm}
Generating negative samples is done by randomly sampling regions of differing scales and positions from the provided training images.
In this process we additionally make sure, none of the proposed negative samples overlapping with any on the ground truth annotations present in the images.
Then we scale these proposed negative samples to \( (128 \times 128 ) \) px and apply the filtering described in the above paragraph to each sample.
Since the negative samples are randomly generated, we can create arbitrary amounts of them. 
For our testing \( \approx15000 \) worked well. 
Additonal information in the exact size of the dataset is shown in \autoref{tab:dataset-stats}

\begin{table}[]
    \centering
    \begin{tabular}{ccc}
        \toprule
        Class name & \#samples & percentage \\
        \midrule
        waldo & 137 &  1.01\% \\
        wenda & 43&  0.32\% \\
        wizard& 27&  0.20\% \\
        negative & 13315&  98.47\% \\
        \bottomrule
    \end{tabular}
    \label{tab:dataset-stats}
    \caption{Dataset statistics for the training}
\end{table}

% Specify how to process the data, how to evaluate the performance (e.g., mAP).
% \begin{table}[ht]
%     \centering
%     \begin{tabular}{l|c|c|c}
%     \hline
%      Dataset & \#train & \#test & \#Category\\
%     \hline
%     MNIST& 60,000 & 10,000 & 10  \\
%     CIFAR-10& 50,000 & 10,000 & 10 \\
%     \hline
%     \end{tabular}
%     \caption{Summary of datasets.}
%     \label{tab:dataset}
% \end{table}

\subsection{Implementation}\label{sec:implemenation}
Give a figure to illustrate your implementation, then detail each parts.
